\begin{abstract}
% Abstract length should not exceed 250 words
% Background
It is difficult to model kinematics of a legged-wheel robot; primarily due to the complex interactions between their irregularly shaped wheels and the ground. Yet, for many applications such models are vital. For example, to predict the current velocity of the robot.
% Methods
We propose using a simulator neural network (SNN) to model the kinematics of a transformable wheel mobile robot. We use a physical simulation of our robot to generate training data, which we in turn use to optimize an SNN that can predict changes to the robot’s pose based on its current control commands.
% Results
The SNN is better able to predict the location of the physically simulated mobile robot when compared to a differential drive model. Using the trained network, we next evolve a simple controller to navigate a series of way-points. Finally, we transferred the evolved control parameters to the physically simulated robot where we see nearly identical behaviors to those of the SNN.
% Conclusions
Our results show that an SNN can be effective for predicting the movement of a transformable wheel mobile robot.
\end{abstract}

% It is difficult to model kinematics of a legged-wheel robot; primarily due to the complex interactions between their irregularly shaped wheels and the ground. Yet, for many applications such models are vital. For example, to predict the current velocity of the robot. We propose using a simulator neural network (SNN) to model the kinematics of a transformable wheel mobile robot. We use a physical simulation of our robot to generate training data, which we in turn use to optimize an SNN that can predict changes to the robot’s pose based on its current control commands. The SNN is better able to predict the location of the physically simulated mobile robot when compared to a differential drive model. Using the trained network, we next evolve a simple controller to navigate a series of way-points. Finally, we transferred the evolved control parameters to the physically simulated robot where we see nearly identical behaviors to those of the SNN. Our results show that an SNN can be effective for predicting the movement of a transformable wheel mobile robot.
